JD-R Theory: Using the Content of the O*Net

### 2022-08-18 SIOP2023/SIOP_PROCESS.Rmd
moving to folders and renaming .Rmd
sourcing process macro as separate script and results table

bibliography      : ["r-references.bib", "SIOP_Onet_FA.bib", "jdr.bib", "jobdemands_resources_bibtex.bib"]

@@

```{r PROCESS}

#Next, try a moderated regression

# PROCESS for R version 4.1.1
# Written by Andrew F. Hayes
# www.afhayes.com
# www.processmacro.org
# Copyright 2012-2022 by Andrew F. Hayes ALL RIGHTS RESERVED
# PROCESS workshop schedule at http://haskayne.ucalgary.ca/CCRAM
#
# Distribution of this code in any form except through processmacro.org 
# is prohibited without the permission of the copyright holder, as is
# distribution after modification.
#
# THIS SOFTWARE IS PROVIDED AS IS, WITHOUT WARRANTY OF ANY KIND
# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
# MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT
# IN NO EVENT SHALL THE COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM
# DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT
# OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE
# SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE
# USE OF THIS SOFTWARE IMPLIES AGREEMENT WITH THESE TERMS
#
# To activate, run this script. It may take a few minutes. 
# Patience is a virtue. This will produce a function called process.
# The other functions it creates cannot be accessed by the user
# but are used by the master process function.

process.bcboot3<-function(databcbt,estmte,xp2,badend,priorlo,priorhi)
{
  databcbt<-as.matrix(sort(databcbt))
  badlo<-0;badhi<-0
  pv<-matrix(as.numeric(databcbt < estmte));
  pv<-sum(pv)/nrow(databcbt);ppv<-pv;
  if (pv > .5){ppv<-(1-pv)}
  y5<-sqrt(-2*log(ppv))
  p0<-(-.322232431088);p1<-(-1);p2<-(-.342242088547);p3<-(-.0204231210245)
  p4<-(-.0000453642210148);q0<-(.0993484626060);q1<-(.588581570495)
  q2<-(.531103462366);q3<-(.103537752850);q4<-(.0038560700634)
  xp<-y5+((((y5*p4+p3)*y5+p2)*y5+p1)*y5+p0)/((((y5*q4+q3)*y5+q2)*y5+q1)*y5+q0)
  if (pv <= .5){xp<-(-xp)}
  cilow<-round(nrow(databcbt)*pnorm(2*xp-xp2))
  cihigh<-trunc(nrow(databcbt)*pnorm(2*xp+xp2))+1
  if (cilow < 1){cilow<-1;booterr<-1;badlo<-1}
  if (cihigh > nrow(databcbt)){cihigh<-nrow(databcbt);booterr<-1;badhi<-1}
  llcit<-databcbt[cilow,1]
  ulcit<-databcbt[cihigh,1]
  if ((badlo==1) & (llcit != priorlo)){priorlo<-llcit;badend<-c(badend,llcit)}
  if ((badhi==1) & (ulcit != priorhi)){priorhi<-ulcit;badend<-c(badend,ulcit)}
  bootse<-sd(databcbt)
  cires<-as.matrix(c(bootse,llcit,ulcit))
  cires<-list(cires,badend,priorlo,priorhi)
  return(cires)
}

process.pboot3<-function(databcbt,lcval,hcval)
{
  databcbt<-as.matrix(sort(databcbt))
  llcit<-databcbt[lcval,1]
  ulcit<-databcbt[hcval,1]
  bootse<-sd(databcbt)
  cires<-as.matrix(c(bootse,llcit,ulcit))
  return(cires)
}

process.llrtest3<-function(lm,y,x,b,basemod,iterate,converge)
{
  lm<-as.matrix(lm)
  btemphld<-b
  llrdat<-matrix(-999,nrow(x),(nrow(lm)-sum(lm)))
  llrdf<-ncol(x)-ncol(llrdat)
  llrcnt<-0
  for (llri in (1:nrow(lm)))
  {
    if (lm[llri,1]==0){llrcnt<-llrcnt+1;llrdat[,llrcnt]<-x[,llri]}
  }
  LL2<-process.modelest(y,llrdat,2,0,xp2,5,iterate,converge)
  b<-btemphld
  pvchi<-(1-pchisq((LL2-basemod),df=llrdf))
  fresult<-cbind((LL2-basemod),llrdf,pvchi)
  return(fresult)
}

process.describ3<-function(descdatf,type=0,quantle=1)
{
  desctmp<-matrix(-999,(8-(4*type)),ncol(descdatf))
  # mean, sd, min, max, 16th, 50th, 84th, dich toggle
  for (jd in c(1:ncol(descdatf)))
  {
    descdat<-descdatf[,jd]
    #get the mean, sd, minimum, and maximum */
    desctmp[1,jd]<-mean(descdat)
    desctmp[2,jd]<-sd(descdat)
    desctmp[3,jd]<-min(descdat)
    desctmp[4,jd]<-max(descdat)
    if (type==0)
    {
      minwarn<-0;maxwarn<-0
      tmp=as.numeric(descdat==desctmp[3,jd])+as.numeric(descdat==desctmp[4,jd])
      desctmp[8,jd]<-as.numeric(sum(tmp)==length(tmp))
      if (desctmp[3,jd]==desctmp[4,jd]){desctmp[8,jd]<-2}
      descdat<-matrix(sort(descdat))
      decval<-c(.16,.5,.84)
      for (kd in c(1:3))
      {
        low<-trunc(decval[kd]*(length(descdat)+1))
        lowdec<-decval[kd]*(length(descdat)+1)-low
        value<-descdat[low,1]+(descdat[(low+1),1]-descdat[low,1])*lowdec
        desctmp[(4+kd),jd]<-value
      }
      mnotev<-(1)
      modvals<-matrix(desctmp[5:7,],ncol=ncol(descdatf))
      if (quantle != 1)
      {
        desctmp[5,jd]<-desctmp[1,jd]-desctmp[2,jd]
        desctmp[6,jd]<-desctmp[1,jd]
        desctmp[7,jd]<-desctmp[1,jd]+desctmp[2,jd]
        modvals<-matrix(desctmp[5:7,],ncol=ncol(descdatf))
        mnotev<-(2)
        if (modvals[1,1] < desctmp[3,1]){modvals[1,1]<-desctmp[3,1];minwarn<-1}
        if (modvals[3,1] > desctmp[4,1]){modvals[3,1]<-desctmp[4,1];maxwarn<-1}
      }
      if (desctmp[8,jd]==1)
      {modvals<-matrix(c(desctmp[3,1],desctmp[4,1]))
      mnotev<-0;minwarn<-0;maxwarn<-0
      }
      descrtrn<-list(desctmp,modvals,minwarn,maxwarn,mnotev)
    }
  }
  if (type==1)
  {descrtrn<-list(desctmp)}
  return(descrtrn)
}

process.ftest3<-function(lm,bcoef,cv=0,chr=0,brsq=0,skip=0,y,x)
{
  lmat2<-as.matrix(lm)
  y<-as.matrix(y)
  x<-as.matrix(x)
  n<-nrow(y)
  if (skip==0)
  {
    lmat2<-as.matrix(diag(as.numeric(lm)))
    lmat3<-matrix(0,nrow(lmat2),1)
    for (flp in c(1:ncol(lmat2)))
    {
      if (sum(lmat2[,flp])==1)
      {lmat3<-cbind(as.matrix(lmat3),as.matrix(lmat2[,flp]))}
    }
    lmat2<-as.matrix(lmat3[,2:ncol(lmat3)])
  }
  fratio<-(t(t(lmat2)%*%bcoef)%*%solve(t(lmat2)%*%cv%*%lmat2)%*%((t(lmat2)%*%bcoef)))/ncol(lmat2)
  pfr<-(1-pf(fratio,ncol(lmat2),(n-nrow(bcoef))))
  fresult<-matrix(c(fratio,ncol(lmat2),(n-nrow(bcoef)),pfr),ncol=4)
  if (chr==1)
  {
    lmat3<-as.matrix(1-rowSums(lmat2))
    xfm<-matrix(0,n,sum(lmat3))
    flpc<-1
    for (flp in (1:nrow(lmat3)))
    {
      if (lmat3[flp,1]==1){xfm[,flpc]=x[,flp];flpc<-flpc+1}
    }
    bfm<-solve(t(xfm)%*%xfm)%*%t(xfm)%*%y
    resid<-y-(xfm%*%bfm)
    sstotal<-t(y-(sum(y)/n))%*%(y-(sum(y)/n))
    ssresid<-t(resid)%*%resid
    rsqch<-as.numeric(brsq)-((sstotal-ssresid)/sstotal)
    fresult<-matrix(c(rsqch,fresult),ncol=5)
  }
  ftestout<-as.matrix(fresult)
  return(ftestout)
}

#type1 for ols, type2 for logistic LLR, type3 for logistic bootstrapping
process.modelest<-function(y,x,type,full,xp2,hc=5,iterate=100,converge=.00001)
{
  if (type==1)
  {
    invxtx<-solve(t(x)%*%x)
    b<-invxtx%*%t(x)%*%y
    modres<-b
    if (full==1)
    {
      n1<-nrow(x)
      dfres<-(n1-(ncol(x)))
      sstotal<-t(y-(sum(y)/n1))%*%(y-(sum(y)/n1))
      resid=y-x%*%b
      ssresid<-sum(t(resid)%*%resid)       
      r2<-(sstotal-ssresid)/sstotal
      adjr2<-(1-((1-r2)*(n1-1)/(dfres)))
      mse<-ssresid/(n1-ncol(x))
      #HC covariance matrix
      varb<-mse*invxtx
      k3<-ncol(x)
      xhc<-0
      if (hc != 5)
      {
        xhc<-x
        hat<-matrix(xhc[,1])
        for (i3 in c(1:nrow(xhc)))
        {
          xhcm<-matrix(xhc[i3,])
          hat[i3,1]<-t(xhcm)%*%invxtx%*%xhcm
        }     
        if ((hc==0) | (hc==1))
        {
          for (i3 in c(1:k3)){xhc[,i3]<-xhc[,i3]*resid}
        }
        if ((hc==3) | (hc==2))
        {
          for (i3 in c(1:k3))
          {xhc[,i3]<-(resid/(1-hat)^(1/(4-hc)))*xhc[,i3]}
        }
        if (hc==4)
        {
          hcmn<-matrix(4,n1,2);hcmn[,2]<-(n1*hat)/k3
          minr<-apply(hcmn,1,FUN=min)
          for (i3 in c(1:k3))
          {
            xhc[,i3]<-(resid/(1-hat)^(minr/2))*xhc[,i3]
          }
        }
        varb<-(invxtx%*%t(xhc)%*%xhc%*%invxtx)
        if (hc==1){varb<-(n1/(n1-ncol(x)))*varb}
      }
      seb<-sqrt(diag(varb))
      trat<-b/seb
      p<-2*pt(-abs(trat),df=dfres)
      tval<-sqrt(dfres* (exp((dfres-(5/6))*((xp2/(dfres-(2/3)+(.11/dfres)))*(xp2/(dfres-(2/3)+(.11/dfres)))))-1))
      modres<-matrix(c(modres,seb, trat,p,(b-tval*seb),(b+tval*seb)),ncol=6)
      modresl<-t(matrix(c("coeff","hclab","t","p","LLCI","ULCI")))
      lmat<-diag(ncol(x));lmat<-lmat[,2:ncol(lmat)]
      fratio<-(t(t(lmat)%*%b)%*%solve(t(lmat)%*%varb%*%lmat)%*%((t(lmat)%*%b)))/(ncol(x)-1)
      pfr<-1-pf(fratio,(ncol(x)-1),dfres)
      modsum=matrix(c(sqrt(r2),r2,mse,fratio,(ncol(x)-1),dfres,pfr))
      modsuml=matrix(c("R","R-sq","MSE","hcflab","df1","df2", "p"))
      modretrn<-list(modres,modresl,modsum,modsuml,b,varb,tval,resid)
      return(modretrn)
    }
    if (full==0){return(modres)} 
  }
  #for logistic Y model
  if ((type==2) | (type==3))
  {
    xlp<-x;ylp<-as.matrix(y)
    pt2<-matrix((sum(ylp)/nrow(ylp)),nrow(ylp),1)
    if ((type==2)|(type==3)) {LL3<-(ylp*log(pt2)+(1-ylp)*log(1-pt2))}    
    LL3<-(-2*sum(LL3))
    bt1<-matrix(0,ncol(xlp),1);LL1<-0
    pt1<-matrix(0.5,nrow(ylp),1);pt1lp<-pt1
    for (jjj in (1:iterate))
    {
      xlptmp<-t(xlp)
      vecprb<-(pt1lp*(1-pt1lp))
      for (kkk in (1:ncol(xlp))){xlptmp[kkk,]<-xlptmp[kkk,]*t(vecprb)}
      b<-bt1+solve(xlptmp%*%xlp)%*%t(xlp)%*%(ylp-pt1lp)
      if ((type==2) | (type==3))
      {
        xlpb<-xlp%*%b
        xlpbt<-as.numeric(xlpb > -709.7)
        xlpb709<-((1-xlpbt)*(-709.7))
        xlpb<-((xlpb*xlpbt)+xlpb709)
        pt1lp<-1/(1+exp(-(xlpb)))
      }
      itprob<-sum((pt1lp < .00000001) | (pt1lp > .9999999))
      if (itprob > 0)
      {
        for (kkk in (1:nrow(pt1lp)))
        {
          if (pt1lp[kkk,1] > .9999999){pt1lp[kkk,1]<-.9999999}     
          if (pt1lp[kkk,1] < .00000001){pt1lp[kkk,1]<-.00000001}     
        }
        itprob<-0
      }
      if (itprob==0)
      {
        if ((type==2)|(type==3)){LL<-(ylp*log(pt1lp)+(1-ylp)*log(1-pt1lp))}
        LL2<-(-2*sum(LL))
      }
      if (abs(LL1-LL2) < converge)
      {
        if (full==1)
        {
          xlptmp<-t(xlp)
          vecprb<-(pt1lp*(1-pt1lp))   
          for (kkk in (1:ncol(xlp))){xlptmp[kkk,]<-xlptmp[kkk,]*t(vecprb)} 
          varb<-solve(xlptmp%*%xlp)
          seb<-matrix(sqrt(diag(varb)))
        }
        break
      }
      bt1<-b;LL1<-LL2
    }
    modres<-b
    if (jjj > iterate)
    {
      itprob<-2
      if (booting==0){iterrmod<-1}   
      if (booting==1){bootiter==1}   
      if (itprobtg==0)
      {   
        itprobtg<-1;errcode[errs,1]<-47;errs<-errs+1
        if ((booting==0) & (full==1))
        {
          pt1lpc<-(pt1lp*(1-pt1lp))
          vt1<-diag(pt1lpc)
          varb<-solve(t(xlp)%*%vt1%*%xlp)
          seb<-matrix(sqrt(diag(varb)))
        }
      }
    }
    if (full==1)
    {
      trat<-b/seb
      dfres<-nrow(xlp)   
      p<-2*(1-pnorm(abs(trat)))
      modres<-cbind(modres,seb,trat,p) 
      modres<-matrix(c(modres,(b-xp2*seb),(b+xp2*seb)),ncol=6)
      pvchi<-(1-pchisq((LL3-LL2),df=(nrow(modres)-1)))
      mcF<-(LL3-LL2)/LL3
      cox<-1-exp(-(LL3-LL2)/nrow(xlp))
      nagel<-cox/(1-exp(-(LL3)/nrow(xlp)))
      modsum<-matrix(c(LL2,(LL3-LL2),(nrow(modres)-1),pvchi, mcF,cox,nagel))
      modsuml<-matrix(c("-2LL","ModelLL", "df", "p", "McFadden", "CoxSnell", "Nagelkrk"))
      modresl<-t(matrix(c("coeff","se","Z","p","LLCI","ULCI")))
      modretrn<-list(modres,modresl,modsum,modsuml,b,varb,xp2)
      return(modretrn)
    }
    if ((full==0) & (type==2)){return(LL2)} 
    if ((full==0) & (type==3)){return(modres)}
  }
}

process.dummy3<-function(dd)
{
  uq<-unique(dd)
  uq<-matrix(unlist(uq[1]))
  dummy<-matrix(0,nrow(dd),nrow(uq))
  uq<-matrix(sort(uq))
  uq2<-matrix(seq(1:nrow(uq)))
  for (i in c(1:nrow(dd)))
  {for (j in c(1:nrow(uq)))
  {if (dd[i,1]==uq[j,1])
  {dummy[i,uq2[j,1]]<-1}  
  }
  }
  return(dummy)
}

process.makdummy<-function(dd,method,custcov=0,custcode=999)
{
  dd<-dd[order(dd[,2]),]
  newrow<-dd[,1]
  dd<-dd[,2]
  dd<-as.data.frame(dd)
  dummy<-process.dummy3(dd)
  uq<-unique(dd);uq<-matrix(unlist(uq[1]))
  criterrd<-0;errcode5<-0;errcode4<-0;errcode6<-0
  nvls<-ncol(dummy)
  nnvls<-colSums(dummy)
  mnvls<-min(nnvls)
  nnvls<-matrix(sort(uq))
  conmat1<-1
  if (mnvls < 2){errcode5<-1;criterrd<-1}
  if (nvls > 9){errcode4<-1;criterrd<-1}
  x<-0;dummat<-0
  if (criterrd==0)
  {
    dumok<-1
    if (method > 0)
    {
      x<-dummy[,2:ncol(dummy)]
      nx<-ncol(x)
      minus1<-matrix(-1,1,ncol(x))
      if (method==4)
      {
        for (k in (1:nrow(dd)))
        {shole<-sum(x[k,])
        if (shole==0)
        {x[k,]<-minus1}}
      }
      if ((method==2) | (method==3) | (method==5))
      {
        for (k in (1:nrow(dd)))
        {shole<-sum(x[k,])
        if (shole > 0)
        {
          for (i in (1:ncol(x)))
          {if (x[k,i]==0){x[k,i]<-1} else{break}
          }
        }
        }
        if (method==3)
        {
          conmat1=c(-8,1,1,1,1,1,1,1,1,0,-7,1,1,1,1,1,1,1,0,0,-6,1,1,1,1,1,1,0,0,0,-5,1,1,1,1,1,0,0,0,0,-4,1,1,1,1,0,0,0,0,0,-3,1,1,1,0,0,0,0,0,0,-2,1,1,0,0,0,0,0,0,0,-1,1)
          conmat1<-t(matrix(conmat1,9,8))
          for (i in (1:8)){conmat1[i,]=conmat1[i,]/(10-i)}
          conmat1<-t(conmat1[(10-nvls):8,(10-nvls):9])
          for (k in (1:nrow(dd)))
          {shole<-sum(x[k,]);x[k,]=conmat1[(shole+1),]}
        }
      }
      if (method==5)
      {
        if (ncol(custcode) != (nvls*(nvls-1)))
        {errcode6<-1}
        if (ncol(custcode)==(nvls*(nvls-1)))
        {
          conmat1<-matrix(0,nvls,(nvls-1));cnt<-1
          for (i in (1:nvls))
          {
            for (k in (1:(nvls-1)))
            {conmat1[i,k]<-custcode[1,cnt];cnt<-cnt+1}
          }
          for (k in (1:nrow(dd))){x[k,]<-conmat1[(sum(x[k,])+1),]}   #check this
        }
      }
      xskip<-1
      dummat<-matrix(0,(nx+1),nx)
      dummat[(2:nrow(dummat)),]<-diag(nx)
      if (method==4){dummat[1,]<-minus1}
      if (method==2)
      {for (i in 2:nrow(dummat))
      {for (j in (1:(i-1))){dummat[i,j]<-1}}
      }
      if (method==3){dummat<-conmat1}
      if ((method==5) & (errcode6==0)){dummat<-conmat1}
      dummat<-cbind(nnvls,dummat)
    } 
    x<-cbind(newrow,x)
    x<-x[order(x[,1]),]
  }
  dummrn<-list(x,dummat,nvls,nnvls,errcode4,errcode5,errcode6)
  return(dummrn)
}

process<-function(data,y="xxxxx",x="xxxxx",m="xxxxx",w="xxxxx",z="xxxxx",cov="xxxxx",
                  model=999,converge=.00001,iterate=100,hc=5,jn=0,effsize=0,stand=0,xmtest=0,normal=0,
                  mdichok=0,contrast=999,modelbt=0,matrices=0,covmy=0,covcoeff=0,boot=5000,mc=0,
                  intprobe=0.1,plot=0,total=0,save=0,mcx=0,mcw=0,mcz=0,moments=0,progress=1,
                  bmatrix=-999,wmatrix=-999,zmatrix=-999,wzmatrix=-999,cmatrix=-999,xcatcode=999,
                  wcatcode=999,zcatcode=999,wmodval=999,zmodval=999,center=0,conf=95,seed=-999,
                  decimals=9.4,maxboot=0,modelres=0,bc=0,outscreen=1,activate=0,describe=0,listmiss=0,
                  linsum=-999)
{

  #all this is initiation of variables and matrices
  ranseed<-0;
  if (seed != -999)
  {seed<-trunc(abs(seed));set.seed(seed)}
  wnames<-w;znames<-z;mcerpt<-0;wiscov<-0;ziscov<-0;itprobtg<-0;
  v2tag<-0;maxwwarn<-0;minwwarn<-0;maxzwarn<-0;minzwarn<-0
  toomany<-0;wdich<-0;zdich<-0;wnotev<-0;znotev<-0;singlr<-0
  nxpval<-1;nwpval<-1;nzpval<-1;errs<-1;notes<-1;criterr<-0
  novar<-0;adjust<-0;ncs<-0;serial<-0;sobelok<-0;hasw<-0;ydich<-0;
  hasz<-0;printw<-0;printz<-0;counterf<-0;wmodcust<-0;zmodcust<-0
  booting<-0;bootiter<-0;iterrmod<-0;model<-trunc(model)
  errcode<-matrix(0,100,1);notecode<-matrix(0,100,1)
  iterate<-abs(trunc(iterate));converge=abs(converge);badend<-0;booterr<-0;
  itprobtg<-0;v2tag<-0;maxwwarn<-0;minwwarn<-0;maxzwarn<-0
  minzwarn<-0;toomany<-0;wdich<-0;zdich<-0;wnotev<-0;znotev<-0
  nws<-0;nzs<-0;nms<-0;nys<-0;nxs<-0;maxresm<-9;bc<-as.numeric(bc==1);progress<-as.numeric(progress==1)
  mcxok<-0;mcwok<-0;mczok<-0;xprod<-0;zprod<-0;wprod<-0;modcok<-0;alttotal=0;bc<-as.numeric(bc==1)
  jn<-as.numeric(jn==1);effsize<-as.numeric(effsize==1);maxboots=abs(trunc(maxboot))
  normal<-as.numeric(normal==1);xmtest<-as.numeric(xmtest==1);modelres<-as.numeric(modelres==1)
  stand<-as.numeric(stand==1);outscreen<-as.numeric(outscreen==1);activate=as.numeric(activate==1)
  describe<-as.numeric(describe==1);listmiss<-as.numeric(listmiss==1);
  if (stand==1) {effsize<-1}
  pstog<-0;sobelok<-0;mdichok=as.numeric(mdichok==1)
  resultm<-matrix(99999,1,maxresm)

  linsum<-t(matrix(linsum));
  nlinsum<-ncol(linsum);
  if (linsum[1,1]==-999){nlinsum<-0}

  #contrast matrix
  contrast<-matrix(contrast);
  contrast<-t(contrast)
  ncontr<-ncol(contrast)
  if (contrast[1,1]==999) {ncontr<-1;contrast[1,1]<-0}
  if (ncontr==1)
  {
    contrast<-trunc(contrast)
    if ((contrast[1,1] > 2) | (contrast[1,1] < 0))
    {ncontr<-1;contrast[1,1]<-0}
  }
  if (ncontr > 1)
  {
    contvec<-contrast;contrast[1,1]<-3
    if (((model==2) | (model==3)) & (nms==0))
    {
      if (ncontr==4)
      {
        contvec<-t(matrix(contvec,2,2))
        contrast[1,1]<-0;modcok<-1;wcontval<-matrix(contvec[,1]);zcontval<-matrix(contvec[,2])
      }
      if (ncontr !=4)
      {
        notecode[notes,1]<-19;notes<-notes+1
        contrast[1,1]<-0
      }
    }
  }
  contrast<-contrast[1,1]
  modelbt<-as.numeric(modelbt==1);matrices<-as.numeric(matrices==1)
  covcoeff<-as.numeric(covcoeff==1);covmy<-trunc(covmy)
  if ((covmy < 0) | (covmy > 2)) {covmy<-0} 
  boot<-abs(trunc(boot));mc=abs(trunc(mc));hc=trunc(hc)
  if ((intprobe < 0) | (intprobe > 1))
  {intprobe<-0.10}
  plot<-trunc(plot)
  if ((plot < 0) | (plot > 2)) {plot<-0}
  total<-as.numeric(total==1)
  dototal<-0
  saveboot<-as.numeric((save==1)|(save==3))
  saveest<-as.numeric(save > 1)
  if (saveest==1){intprobe=1}
  if ((hc >=0) & (hc < 5)) {notecode[notes,1]=4;notes=notes+1}
  if ((hc > 5) | (hc < 0)) {hc=5}
  ####dont use these when y is dichotomous
  hclab<-matrix(c("se(HC0)","se(HC1)","se(HC2)","se(HC3)","se(HC4)","se"))
  hclab<-hclab[(hc+1),1]
  hcflab<-matrix(c("F(HC0)","F(HC1)","F(HC2)","F(HC3)","F(HC4)","F"))
  hcflab<-hcflab[(hc+1),1] 
  mcw=trunc(mcw);mcz=trunc(mcz);mcx=trunc(mcx);
  if ((mcx > 0) & (model==74)) {mcw=mcx}
  if ((mcw > 0) & (model==74)) {mcx=mcw}
  if ((mcx > 0) & (contrast > 0))
  {notecode[notes,1]=28;notes=notes+1;contrast=0};
  nxvls<-1;nmvls<-1;nwvls<-1;nzvls<-1
  paths<-matrix(999);pathsw<-matrix(999);pathsz<-matrix(999);
  pathswz<-matrix(999);pathsmod<-matrix(999);pathtype<-matrix(999);obscoeff<-999;
  pathsdv=matrix(" ");quantile<-1;moments=as.numeric(moments==1)
  if (moments==1){quantile<-0}
  bmatrix=t(matrix(bmatrix));wmatrix=t(matrix(wmatrix));zmatrix=t(matrix(zmatrix));
  wzmatrix=t(matrix(wzmatrix));cmatrix=t(matrix(cmatrix));xcatcode=t(matrix(xcatcode));
  wcatcode=t(matrix(wcatcode));zcatcode=t(matrix(zcatcode));
  needed<-0
  decimals<-paste("%",decimals,"f",sep='')
  if ((trunc(conf) >= 100) | (trunc(conf <= 50)))
  {conf=95;notecode[notes,1]=2;notes=notes+1}
  if ((model >= 0)  & (model < 4) & (modelbt==0)) {boot<-0;mc<-0;bc<-0;saveboot<-0}
  if ((boot > 0) & (mc > 0)) {boot<-0;bc<-0}
  if ((boot < 1000) & (boot > 0) & (mc==0)){boot=5000}
  if ((mc < 1000) & (mc > 0) & (boot==0)){mc=5000}

  #if ((model > 0) & (model < 4) & (boot = 98765) & (modelbt=1)) then;do;mc=0;boot=5000;end;
  #if ((model > 0) & (model < 4) & ((boot = 98765) | (mc > 0))) then;do;boot=0;mc=0;bc=0;end;
  #if ((boot = 98765) & (mc = 0)) then;do;boot=5000;end;

  p0<- -.322232431088;p1<- -1;p2<- -.342242088547;p3<- -.0204231210245;
  p4<- -.0000453642210148;q0<- .0993484626060;q1<- .588581570495;
  q2<- .531103462366;q3<- .103537752850;q4<- .0038560700634;
  priorlo<-(-9999999);priorhi<-9999999
  alpha2<-(1-(conf/100))/2;cilm<-alpha2*2;y5<-sqrt(-2*log(alpha2));
  xp2=(y5+((((y5*p4+p3)*y5+p2)*y5+p1)*y5+p0)/((((y5*q4+q3)*y5+q2)*y5+q1)*y5+q0))
  medlb=matrix(c("   M1 :","   M2 :","   M3 :","   M4 :","   M5 :","   M6 :","   M7 :","   M8 :","   M9 :","  M10 :"))
  medlb2=matrix(c("(M1)","(M2)","(M3)","(M4)","(M5)","(M6)","(M7)","(M8)","(M9)","(M10)"))
  xlb=matrix(c("X1 :","X2 :","X3 :","X4 :","X5 :","X6 :","X7 :","X8 :","X9 :","X10:"))
  highlbw=matrix(c("M1*W","M2*W","M3*W","M4*W","M5*W","M6*W","M7*W","M8*W","M9*W","M10*W"))
  highlbz=matrix(c("M1*Z","M2*Z","M3*Z","M4*Z","M5*Z","M6*Z","M7*Z","M8*Z","M9*Z","M10*Z"))
  highlbwz=matrix(c("M1*W*Z","M2*W*Z","M3*W*Z","M4*W*Z","M5*W*Z","M6*W*Z","M7*W*Z","M8*W*Z","M9*W*Z","M10*W*Z"))
  highlbx=matrix(c("M1*X","M2*X","M3*X","M4*X","M5*X","M6*X","M7*X","M8*X","M9*X","M10*X"))
  highlbbt=matrix(c("BOTH(M1)","BOTH(M2)","BOTH(M3)","BOTH(M4)","BOTH(M5)","BOTH(M6)","BOTH(M7)","BOTH(M8)","BOTH(M9)","BTH(M10)"))
  skipwz=0
  xnck=matrix(x);ynck=matrix(y);wnck=matrix(w);znck=matrix(z);mnck=matrix(m);cnck=matrix(cov)
  if ((nrow(xnck)>1) | (nrow(ynck)>1) | (nrow(wnck)>1) | (nrow(znck)>1))
  {errcode[errs,1]<-3;errs<-errs+1;criterr<-1}

  validm=matrix(c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,1,1,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1))
  dim(validm)<-c(1,92)

  # check for major errors in syntax
  if (activate==1)
  {errcode[errs,1]<-60;errs<-errs+1;criterr<-1}
  if (criterr==0)
  {
    if ((model > 0) & (model < 93))
    {
      if (validm[1,model]==0)
      {
        errcode[errs,1]<-6;errs<-errs+1;criterr<-1
      }
    }
    if (((model > 92) | (model < 0)) & (model != 999))
    {errcode[errs,1]<-7;errs<-errs+1;criterr<-1}
    if ((model==999) & (bmatrix[1,1]==-999))
    {errcode[errs,1]<-24;errs<-errs+1;criterr<-1}
    if ((model != 999) & (bmatrix[1,1] != -999))
    {errcode[errs,1]<-25;errs<-errs+1;criterr<-1}
    if (((model==74) | ((model > 0) & (model < 4))) & ((wmatrix[1,1] !=-999) | (zmatrix[1,1] != -999) | (wzmatrix[1,1] != -999)))
    {errcode[errs,1]<-41;errs<-errs+1;criterr<-1}
    if ((y=="xxxxx") | (x=="xxxxx"))
    {errcode[errs,1]<-1;errs<-errs+1;criterr<-1}
    if ((mnck[1,1]=="xxxxx") & (model > 3))
    {errcode[errs,1]<-8;errs<-errs+1;criterr<-1}
  } 
  #end of check for major errors in syntax

  #A loop reads data and does some other things

  if (criterr==0)
  {
    #read y data
    ytmp<-data[y];nys<-ncol(ytmp);needed<-nys
    ynames<-matrix(y);n<-nrow(ytmp);varnames<-matrix(ynames)
    dat<-ytmp
    modelvar<-matrix(c(model,ynames))
    if (model==999){modelvar[1,1]="CUSTOM"}

    #read x data
    xtmp<-data[x];
    nxs<-ncol(xtmp);needed<-needed+nxs;
    dat<-cbind(dat,xtmp)
    xnames<-matrix(x);n<-nrow(xtmp);xcatlab<-xnames;
    varnames<-matrix(c(varnames,xnames))
    modelvar<-matrix(c(modelvar,xnames))
    if (nxs==1){modelvlb<-matrix(c("Model :","    Y :","    X :"))}

    #read m data
    if (mnck[1,1] != "xxxxx")
    {
      mtmp<-data[m]
      nms<-ncol(mtmp)
      mnames<-matrix(m)
      mprod<-matrix(0,1,nms)
      n<-nrow(mtmp)
      needed<-needed+nms
      varnames<-matrix(c(varnames,mnames))
      dat<-cbind(dat,mtmp)
      modelvar<-matrix(c(modelvar,mnames))
      x2m<-matrix(0,99,nms)
      x2m<-matrix(0,99,nms)
      x2y<-matrix(0,99,nms)
      onem<-matrix(1,nms,1)
      if ((nms > 1) & (nms < 11))
      {modelvlb<-matrix(c(modelvlb,medlb[1:nms,1]))}
      if (nms==1)
      {modelvlb<-matrix(c(modelvlb,"    M :"))}
      if ((nms > 0) & (model < 4)){errcode[errs,1]<-9;errs<-errs+1;criterr<-1}
    }

    #read w data
    wlocatet<-0;wlocate<-0
    if (w != "xxxxx")
    {
      wtmp<-data[w];nws=ncol(wtmp);n<-nrow(wtmp)
      dat<-cbind(dat,wtmp)
      wnames<-matrix(w);wcatlab<-wnames;
      varnames<-matrix(c(varnames,wnames))
      modelvar<-matrix(c(modelvar,wnames))
      modelvlb<-matrix(c(modelvlb,"    W :"))
      wlocate<-nrow(varnames)
      if (model==74)
      {
        wlocatet<-1;
        if (xnames != wnames)
        {errcode[errs,1]<-45;errs<-errs+1;criterr<-1}
      }     
    }

    #read z data
    if (z != "xxxxx")
    {
      ztmp<-data[z];nzs<-ncol(ztmp);n<-nrow(ztmp);
      dat<-cbind(dat,ztmp)
      znames<-matrix(z);zcatlab<-znames;
      varnames<-matrix(c(varnames,znames))
      modelvar<-matrix(c(modelvar,znames))
      modelvlb<-matrix(c(modelvlb,"    Z :"))
    }

    #read cov data
    if (cnck[1,1] != "xxxxx")
    {
      ctmp<-data[cov];ncs<-ncol(ctmp);n<-nrow(ctmp);
      dat<-cbind(dat,ctmp)
      covnames<-matrix(cov);varnames<-matrix(c(varnames,covnames));  
    }

    if (((model==80) | (model==81)) & ((nms < 3) | (nms > 6)))
    {errcode[errs,1]<-32;errs<-errs+1;criterr<-1}
    if ((model==82) & (nms != 4))
    {errcode[errs,1]<-33;errs<-errs+1;criterr<-1}
    if (nms > 10)
    {errcode[errs,1]<-37;errs<-errs+1;criterr<-1}
    if (((model==6) | ((model > 82) & (model < 999))) & ((nms < 2) | (nms > 6)))
    {errcode[errs,1]<-34;errs<-errs+1;criterr<-1}

>>>>

bibliography      : ["r-references.bib", "SIOP_PROCESS.bib", "jdr.bib", "jobdemands_resources_bibtex.bib"]

@@

```{r PROCESS, include=FALSE}

source("process.R", local = knitr::knit_global())
